### 2019-12-03 Mathematical Statistics/04_sampling_distributions.rmd
mathematical statistics, ch4 work
mathematical statistics, ch4 work

@@

@@

@@

@@

What proportion of the sample means is as large or larger than 12?

@@

@@

@@

@@

@@

@@

@@

@@

@@

b.) Simulate the sampling distribution in R and plot your results. Check that the simulated mean and standard error are close to the exact mean and standard error.

@@

>>>>

The sampling distribution of $\hat{p}$ is approximately normal with:

@@

n <- 800
mu <- .286

ev <- 800 * mu
sigma <- sqrt(n*mu*(1-mu))

@@

$\mathbb{E}[X] = `r ev`$ and $\sigma = \sqrt{800(.286)(1 - .286)} = `r round(sigma, 4)`$

l <- pnorm((ev - 219.5) / sigma)
h <- pnorm((ev - 230.5) / sigma)

p <- l - h

Probability: `r round(p, 4)`

@@

$X \sim Exp(\frac{1}{10}), \mathbb{E}(x) = 10$

@@

```{r, echo = T, fig.height=3.5, fig.width=12}

N <- 1000
result <- numeric(N)

for( i in 1:N)
{
   samp <- rexp( n = 30, rate = 1/10)
   result[i] <- mean(samp)
}

ggplot(data.table(result), aes(result)) +
   geom_histogram(aes(y = ..density.., fill = ..count..), bins = 30) +
   geom_vline(xintercept = 12, col = "darkorange") +
   stat_density( kernel = "gaussian", fill = "darkorange", alpha = .3) +
   labs(title = "Exp(1/10) Sampling Distribution")

p <- mean(result > 12)

What proportion of the sample means is as large or larger than 12? __`r p*100`%__

@@

__Yes__, only ~13% of the sample means have a value of 12 or higher.

@@

$W \sim N(7, 5^2)$

@@

X <- rnorm(10e3, 15, 3)
Y <- rnorm(10e3, 4, 2)

W <- X - 2*Y

ggplot(data.table(x = W)) +
   geom_histogram(aes(x, fill = ..count..), bins = 30) +
   geom_vline(xintercept = 7, col = "darkorange", lwd = 1.5) +
   scale_y_continuous(labels = comma) +
   labs(title = "Sampling Distribution")

@@

```{r, echo = T}
mu <- mean(W)
sigma <- sd(W)
```

@@

```{r, echo = T}
phat <- mean(W <= 10)

p <- pnorm(10, mean = 7, sd = 5)

$\hat{p}= `r phat*100`$%

$P(W \le 10) = `r round(p, 4)*100`$%

@@

$W \sim Pois(19)$

@@

```{r, echo = T, fig.height=3.5, fig.width=8}
W <- rpois(10e3, lambda = 19)

ggplot(data.table(x = W)) +
   geom_histogram(aes(x, fill = ..count..), bins = 30) +
   geom_vline(xintercept = 19, col = "darkorange", lwd = 1.5) +
   scale_y_continuous(labels = comma) +
   labs(title = "Sampling Distribution")

@@

```{r, echo = T}
phat <- mean(W <= 14)

p <- ppois(14, lambda = 19)

$\hat{p} = `r phat*100`$%

$P(W \le 14) = `r round(p, 4)*100`$%

@@

$W \sim N(36, 3.1^2)$

b.) Simulate the sampling distribution in R and plot your results.

N <- 10e3
result <- numeric(N)

for( i in 1:N)
{
   X <- rnorm(10, 20, 8)
   Y <- rnorm(15, 16, 7)

   result[i] <- mean(X) + mean(Y)
}

ggplot(data.table(x = result)) +
   geom_histogram(aes(x, fill = ..count..), bins = 30) +
   geom_vline(xintercept = 36, col = "darkorange", lwd = 1.5) +
   scale_y_continuous(labels = comma) +
   labs(title = "Sampling Distribution")

Check that the simulated mean and standard error are close to the exact mean and standard error.

```{r, echo = T}
mu <- mean(result)
sigma <- sd(result)
```

@@

```{r, echo = T}
phat <- mean(result <= 40)

p <- pnorm(40, 36, 3)
```

$\hat{p} = `r phat*100`$%

$P(W < 40) = `r round(p, 4)*100`$%
